How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
Reworded Fixed conclusion

By inspecting graphs of the performances of individual configurations for each type annotation, we can see type annotations that likely have a significant effect on performance. By then inspecting the typing lattice graphs colour coded for such type annotations, we were often able to notice patterns which suggested that just one or two of the type annotations were likely responsible for the bimodal performance. Though every type annotation that appeared to have a significant effect across the typing lattice also showed a singificant performance effect when no other typing annotations where present, the converse did not hold. In particular, the type annotations we identified appear to be responsible for most of the overhead caused by Moth's transient type checking.

>>>>

By inspecting graphs of the performance of where only one type annotation is present, we can easily identify type annotations that likely have a significant effect on performance. By then inspecting the typing lattice graphs colour coded based on whether such type annotation was present or not, we were often able to notice patterns. In particular, these patterns suggested the just one or type type annotations are likely responsible for the bimodal performance and most of the overhead caused by Moth's transient type checking. Though every type annotation that appeared to have a significant effect across the typing lattice also showed a significant performance effect when no other typing annotations where present, the converse did not hold.
